---
title: "restfulSEData -- SummarizedExperiment shells for remote assay data"
author: "Vincent J. Carey, stvjc at channing.harvard.edu, Shweta Gopaulakrishnan reshg at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{restfulSEData -- SummarizedExperiment shells for remote assay data}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::pdf_document:
    toc: yes
    number_sections: yes
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

This package includes SummarizedExperiment or RangedSummarizedExperiment
instances from which assay data has been removed, so that it
can be restored in real time from remote stores.

- The example given below elaborates on how to access the data from the standard ExperimentHub interface :  

```{r get-data}
library(ExperimentHub)
ehub = ExperimentHub()
myfiles <- query(ehub , "restfulSEData")
myfiles
myfiles[[1]]
myfiles[["EH551"]] #load by EH id

```

- To get a flavor of the datasets present : 

```{r meta}
dataResource()
```

- To use the data with "restfulSE" R package :
We grab the ExperimentHub ID of the dataset we are interested in. 

```{use data}

myfiles[["EH551"]] -> banoSEMeta
banoSEMeta
```



